---
title: "HW1_Sloppy_Printer"
author: "Tingrui Huang"
date: "September 16, 2018"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

Sloppy Pinter Problem -

```{r}
#Adding image
image_book = 'https://elgarblog.files.wordpress.com/2014/01/education-books.jpg'
if (!file.exists(image <- 'education-books.jpg'))
  download.file(image_book,image,mode = 'wb')
knitr::include_graphics(if(identical(knitr:::pandoc_to(),'html')) image_book else image)
```
Step 1. Understand background information
We have known the average errors the printer makes is 2, therefore we assume the distribution of the number of misprints on each page would be a Poisson distribution with $\lambda$ =2
  Poisson Distribution - $P\left( x \right) = \frac{{e^{ - \lambda } \lambda ^x }}{{x!}}$

In this problem, we are going to figure out the probability P_k of the situation when there are more than k misprints on each page:
  therefore, P_k=1-ppois(k, lambda=2)


Step 2. Modeling in R

```{r }
options(digits = 3)
options(scipen = 999)
#Assume the range of misprints per page is [0,8], total page = 50
k <- c(0:8)
pages <- c(1:51)

#Use Poisson Distribution to estimate the number of misprints per page
misp_1 <- ppois(k,2)
misp_2 <- dpois(k,2)

#Create temporary tables for storing data points in loop
temptab <- rep(NULL,51)
over_k <- c()

#Calculate number of errors for each pages and how many pages has errors larger than n.
for (i in 1:9) {
  for (j in 1:51) {
    misp_ep <- misp_1[i]
    over_k[j] <- pbinom(j,50,misp_ep)-pbinom(j-1,50,misp_ep)
  }
  temptab <- cbind(temptab,over_k)
}

#Build a data frame and transfer data from the temporary table to here.
sumtab <- as.data.frame(temptab, row.names(pages))
  header <- paste(k, "misprints", sep = "")
  colnames(sumtab) = header
  
#Refine the table by using Kable
kable(sumtab)

```

